--- 
title       : Tooth Growth 
subtitle    : Some Exploratory Analysis
author      : Pilar Liria
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [ggplot2, psych, datasets, reshape, xtable, RColorBrewer]  
ext_widgets : {rCharts: ["libraries/nvd3", "libraries/highlights"]} 
mode        : selfcontained # {standalone, draft}
--- 

## Introduction

This document analyzes the **ToothGrowth** data in the R datasets pacakage. The goal of  this report is to show the effect of vitamina C on Tooth Growth in guinea pigs. 

The document includes multiBarchar (instead of Boxplot)  and some summary reports related with the data. 

## Data

The data **ToothGrowth**, consists in 60 observations of 3 variables. The variables are:

1. *len* which is tooth length (it is the *response variable*)
2. *supp* is the way in which the supplement was administered. The levels are *OJ (as orange juice)*, and *VC (as ascorbic acid)*.
3. *dose* of the supplement in miligrams (0.5, 1.0, and 2.0)

---

### MultiBarChart: Tooth Length and the Effect of Vitamin C

```{r  echo=TRUE, results = 'asis'}
require(rCharts)
ToGr = as.data.frame(ToothGrowth)
n1 <- nPlot(len ~ dose, group = 'supp', type = 'multiBarChart',
  data = ToGr)
n1$chart(margin = list(left = 100))
n1$chart(reduceXTicks = FALSE)
n1$xAxis(staggerLabels = TRUE)
n1$xAxis(axisLabel = 'Dose')
n1$yAxis(axisLabel = "Tooth Length")
n1$chart(color = c('orange', 'lightblue'))
## n1$set(width = 400)
n1$save('n1.html', cdn=TRUE)
n1$print("chart1", include_assets=TRUE, cdn=TRUE)
##cat('<iframe src="n1.html" width=75%, height=400></iframe>')
#n1
```

---

### Summary: describeBy

```{r echo=TRUE, results = 'asis'}

    # dB<- describeBy(ToGr$len, group=ToGr$supp, mat=TRUE, digits=2)
    dB<- describeBy(ToGr$len, list(ToGr$supp, ToGr$dose), mat=TRUE, digits=2)
    dB1<-dB[, 1:8]
    print(xtable(dB1), type="html")
    dB2<-dB[, 9:15]
    print(xtable(dB2), type="html")
```

---

### Summary: summary

```{r echo=F, results = 'asis'}
    su<-summary(ToGr)
    print(xtable(su), type="html")
```


### Conclusions

The graph in the slide 3 shows some kind of trend. It looks like as the dose is increased , the tooth length is bigger. When the dose is 0.5 miligrams or 1 miligrams, the length of the tooth with OJ supplement  looks  biger. However if the supplement is 2.0 miligrams, the contrary occurs. 

